INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION

### 2016-09-13 paper.tex
bit of extra intro text

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Philemon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    Robustness of a speech recognition system is a challenging task and modern
    automatic speech recognition (ASR) systems need to be robust to different recording conditions,
    microphone type, accents, and noisy recording environment. We mitigate
    this problem in a fashion similar to recent research on image generation using
    Generative Adversarial Networks and domain adaptation ideas extending
    adversarial gradient-based training.
    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as gender and noise type. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on the Aurora4 dataset.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

\section{Generative Adversarial Networks}
\label{sec:gans}
    One of the most insightful recent advantages in the area of generative models
    is the models of the family of generative adversarial networks (GAN).
    A GAN consists of two networks: generator and discriminator. The generator 
    network $G$ has an
    input of randomly generated vector and is asked to produce an image 
    similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set, the task of the discriminator is to distinguish
    between a generated image and a ``real'' image taken from the dataset. Thus
    the discriminator is just a classifier network with a sigmoid output
    and can be trained with the gradient methods (see 
    Section~\ref{sec:optimization}). The main idea of the generative adversarial
    training is that it is possible to propagate the gradient of the discriminator
    network further to the the generator network staking them on top of each other.
    This leads to an efficient training procedure and GANs achieve the state of the
    art that time on handwritten digit generation MNIST dataset.

    In other words, these two networks are competing with each other the 
    generator is trying to deceive a the discriminator network while it tries
    to do its best to recognize if there was a deception. This game theoretical
    similarity gave a name of adversarial networks. The objective of adversarial
    training is following
    \begin{align*}
        \min_G \max_D V(D, G) = \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
          \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

    One of the properties of GAN networks that there is no straightforward way 
    to evaluate the quality of image generation process since the GAN doesn't 
    output the loglikelihood of its samples. The paper estimated the likelihood
    using the Parzen windows estimator.

>>>>

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Philemon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    Robustness of a speech recognition system is a challenging task and modern
    automatic speech recognition (ASR) systems need to be robust to different recording conditions,
    microphone type, accents, and noisy recording environment. We mitigate
    this problem in a fashion similar to recent research on image generation using
    Generative Adversarial Networks and domain adaptation ideas extending
    adversarial gradient-based training.
    This work focuses on investigation of neural architectures which produce
    representations invariant to certain conditions as gender and noise type. We
    experimentally evaluate proposed architectures on the acoustic modelling task
    for speech recognition on the Aurora4 dataset.
\end{abstract}
%
\begin{keywords}
speech recognition, deep neural networks, invariant representations, adversarial training
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
    One of the most challenging aspects of automatic speech recognition (ASR),
    is the mismatch between the training and testing conditions. During
    testing, a system may encounter new recording conditions, microphone types,
    accents and types of background noises. Even if all testing conditions also appeared
    in the train data, their relative distribution is likely to be
    different. For this reason, it's important to develop systems that are
    robust towards changes in recording conditions in general.

    While many types of model and feature based adaptation methods like MLLR and fMLLR
    \cite{leggetter1995maximum} have been proposed, most of these methods have
    been designed with GMM-HMM systems in mind. Since the enormous success of
    Deep Neural Network (DNN) systems for ASR \cite{hinton2012deep}, GMM-based
    model adaptation is not possible anymore, while feature-based methods may
    not be optimal anymore.
    Moreover, the discriminative gradient-based optimization used to train
    DNNs, in combination with the ability of DNNs to learn highly non-linear
    feature transformations, allows for more flexibility when it comes to the
    construction of training objectives that promote domain invariant
    representations.

@@

\section{Generative Adversarial Networks}
\label{sec:gans}
    One of the most insightful recent advantages in the area of generative models
    is the models of the family of generative adversarial networks (GAN).
    A GAN consists of two networks: generator and discriminator. The generator 
    network $G$ has an
    input of randomly generated vector and is asked to produce an image 
    similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set, the task of the discriminator is to distinguish
    between a generated image and a ``real'' image taken from the dataset. Thus
    the discriminator is just a classifier network with a sigmoid output
    and can be trained with the gradient methods (see 
    Section~\ref{sec:optimization}). The main idea of the generative adversarial
    training is that it is possible to propagate the gradient of the discriminator
    network further to the generator network staking them on top of each other.
    This leads to an efficient training procedure and GANs achieve the state of the
    art that time on handwritten digit generation MNIST dataset.

    In other words, these two networks are competing with each other the 
    generator is trying to deceive the discriminator network while it tries
    to do its best to recognize if there was a deception. This game theoretical
    similarity gave a name of adversarial networks. The objective of adversarial
    training is following
    \begin{align*}
        \min_G \max_D V(D, G) = \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
          \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

    One of the properties of GAN networks that there is no straightforward way 
    to evaluate the quality of image generation process since the GAN doesn't 
    output the log-likelihood of its samples. The paper estimated the likelihood
    using the Parzen windows estimator.
